paper3

### 2022-06-28 paper3.Rmd
objective function for multi-classification

>>>>

```{python}
# https://notebooks.githubusercontent.com/view/ipynb?browser=chrome&color_mode=auto&commit=daa2504c337a74778632d44834209425cb6d357f&device=unknown&enc_url=68747470733a2f2f7261772e67697468756275736572636f6e74656e742e636f6d2f4d696c6164536861686964692f46726175642d446574656374696f6e2d5847426f6f73742f646161323530346333333761373437373836333264343438333432303934323563623664333537662f5847426f6f73745f46726175645f446574656374696f6e2e6970796e62&logged_in=false&nwo=MiladShahidi%2FFraud-Detection-XGBoost&path=XGBoost_Fraud_Detection.ipynb&platform=android&repository_id=152300978&repository_type=Repository&version=98
def objective(params, X, y, X_early_stop, y_early_stop, scorer, n_folds = 10):

    pos_count = y_train.sum()
    neg_count = len(y_train) - pos_count
    imbalance_ratio = neg_count / pos_count

    xgb_clf = XGBClassifier(**params, scale_pos_weight=imbalance_ratio,
                            n_estimators = 2000, n_jobs = 1)

    xgb_fit_params = {'early_stopping_rounds': 50,
                      'eval_metric': ['logloss'],
                      'eval_set': [(X_early_stop, y_early_stop)],
                      'verbose': False
                      }

    cv_score = np.mean(cross_val_score(xgb_clf, X_train, y_train, cv = n_folds,
                               fit_params = xgb_fit_params, n_jobs = -1,
                               scoring = scorer))

    # hypoeropt minimizes the loss, hence the minus sign behind cv_score
    return {'loss': -cv_score, 'status': hyperopt.STATUS_OK, 'params': params}
```
